---
title: "main"
author: "nwfried"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Initialise libraries
```{r}
library(tidyverse)
library("ivreg")
```

Translating do-file "explore_newspaper_msa.do" using https://www.matthieugomez.com/statar/manipulate-data.html and google/chatgpt to build dataset of withdrawn/completed highways.
```{r}
#Read in first dataset, withdrawn
folder <- "data"
data1 <- read_csv(file.path(folder, "hwys2msa.csv")) %>% 
  filter(withdrawal == 1) %>%
  select(msa = smsacode, length, withdrawal)

#Read in second dataset, completed
data2 <- read_csv(file.path(folder, "pr5112msa.csv")) %>%
  filter(!is.na(smsacode),OPEN90!= 0) %>%
  select(msa = smsacode, length = length_in_km, starts_with("OPEN")) %>%
  mutate(withdrawal = 0)


withdrawncombined <- bind_rows(data1, data2)

#sort
withdrawncombined <- arrange(withdrawncombined, msa, withdrawal)

withdrawncombined <- withdrawncombined %>%
  group_by(msa) %>%
  mutate(has_withdraw = max(withdrawal)) %>%
  ungroup()

withdrawncombined <- withdrawncombined %>%
  group_by(msa, withdrawal) %>%
  summarize(length = sum(length, na.rm = TRUE), .groups = 'drop')

# Calculate total length for each msa
withdrawncombined <- withdrawncombined %>%
  group_by(msa) %>%
  mutate(total_length = sum(length, na.rm = TRUE)) %>%
  ungroup()

# Generate frac_length and handle precision issues
withdrawncombined <- withdrawncombined %>%
  mutate(frac_length = length / total_length,
         frac_length = ifelse(frac_length > 0.9999, 1, frac_length))

# Sort by msa and descending withdrawal
withdrawncombined <- withdrawncombined %>%
  arrange(msa, desc(withdrawal))

# Tagging the first occurrence of each msa
withdrawncombined <- withdrawncombined %>%
  group_by(msa) %>%
  filter(row_number() == 1) %>%
  ungroup()

# Replace frac_length with 0 where withdrawal is 0
withdrawncombined <- withdrawncombined %>%
  mutate(frac_length = ifelse(withdrawal == 0, 0, frac_length))

# Drop columns withdrawal, tag, and length
msahwy <- withdrawncombined %>%
  select(-withdrawal, -length) %>%
  rename(frac_length_withdrawn = frac_length)

# Save the final dataframe to a CSV file
write_csv(msahwy, file.path(folder, "msahwy.csv"))

# Display the final dataframe
print(msahwy)
```
The rest of the dofile deals with what we did in the fuzzy_match repo. So we can just read in that data:
```{r}
gentzkowcensus <- read_csv(file.path(folder, "MergedGentzkowCensus.csv"))
#add circulation data
gentzkow <- read.delim(file.path(folder, "30261-0007-Data.tsv")) %>% 
  filter(year == 1960) %>% 
  select(citypermid, numdailies, circ, circ_polaff_R, circ_polaff_I, circ_polaff_D, circ_polaff_none, circ_exlast, circ_exnext)
gentzkowcensus <- left_join(gentzkowcensus, gentzkow, by = join_by(citypermid)) %>%
  rename(msa = smsacode)
#add population information
population <- read_csv(file.path("data/nhgis0034_csv/nhgis0034_ds94_1970_place.csv")) %>%
  select(GISJOIN, population = CBC001)
```
Add population information to this dataset and then merge in with highway data. Generate circulation per capita newspaper info.
```{r}
# merge with hwys2 and msahwy
bygis <- join_by(GISJOIN)
gentzkowcensushwy <- left_join(gentzkowcensus, population, bygis) %>% 
  filter(!is.na(numdailies)) %>%
  filter(population!=0)
# Generate new variables for circulation per capita
gentzkowcensushwy <- gentzkowcensushwy %>%
  mutate(
    circ_per_cap = gentzkowcensushwy$circ / population,
    circ_per_cap_r = gentzkowcensushwy$circ_polaff_R / population,
    circ_per_cap_d = gentzkowcensushwy$circ_polaff_D / population,
    circ_per_cap_i = gentzkowcensushwy$circ_polaff_I / population,
    circ_per_cap_none = gentzkowcensushwy$circ_polaff_none / population
  )
bymsa <- join_by(msa)
gentzkowcensushwy <- inner_join(gentzkowcensushwy, msahwy) %>%
  mutate(lpop = log(population)) %>%
  filter(!is.na(circ_per_cap))
#final dataframe will be named news_hwy for ease of reference
news_hwy <- gentzkowcensushwy
```



Now we can do some OLS Regressions:
```{r}
ols1 <- lm(frac_length_withdrawn ~ circ_per_cap, data = news_hwy)
summary(ols1)
ols2 <- lm(frac_length_withdrawn ~ circ_per_cap + lpop, data = news_hwy)
summary(ols2)
ols3 <-lm(frac_length_withdrawn ~ circ_per_cap_r, data = news_hwy)
summary(ols3)
ols4 <- lm(frac_length_withdrawn ~ circ_per_cap + circ_per_cap_r + circ_per_cap_d + circ_per_cap_i + lpop, data = news_hwy)
summary(ols4)
summary(lm(frac_length_withdrawn ~ circ_per_cap + circ_per_cap_r + circ_per_cap_d + circ_per_cap_i + lpop + numdailies, data = gentzkowcensushwy))
```

